Weather classification using Convolutional Neural Networks

### 2020-01-26 msc_english_contents.tex
update contents

\section{Structure of thesis}
A lot of cool chapters here :))))))

\chapter{Survey of approaches to similar problems}
How did the others do
\section{Non-neural}
Some cool old school pixel approaches
\section{CNN / Pretrained CNN}
How did they train their model
\section{Video}
How to use video

\chapter{Neural networks}
Yes go through CNN, LSTM, Attention
\section{Convolutional Neural Networks}
CNN VERY COOL THING

\subsection{Transfer learning}
How to transfer learning
\subsection{ResNets and VGGNets and other architectures}
Describe them
\section{Recurrent Neural Networks}
LSTMs extremely cool
\subsection{Combining in video}
Video very cool
\section{Attention}
Attention huh

\chapter{Dataset}
Describing our data
\section{Semi-supervised learning}

\chapter{Experiments}
Here are our experiments
\section{Training process}
\subsection{Evaluation criteria}
eval
\subsection{Mixed precision training}
16 bit  masters
\section{Image classifiers}
Only use images
\subsection{Only transfer learned classifier}
Just a ResNet or something
\subsection{Image classifier with attention}
Add attention to image classifier
\section{Video classification}
\subsection{LSTM over video}
just lstm
\subsection{Attention over video}
Attention over video here

\chapter{Result analysis}
Very good models

\chapter{Future work}
How to make it better

@@

@misc{knuthwebsite,
    author    = "Donald Knuth",
    title     = "Knuth: Computers and Typesetting",
    url       = "http://www-cs-faculty.stanford.edu/%7Eknuth/abcde.html"
}
\end{verbatim}

>>>>

\section{Structure of thesis}
Cool stuff etc.

\chapter{Neural networks}
Background stuff 
\section{Fully Connected Networks}
When needed, when good/bad
\section{Convolutional Neural Networks}
Show some basic CNN things maybe
\subsection{Neural image processing}
How it different from classical features and how it works
\section{Attention}
Attention huh
\section{Multi-task learning}
Describe how a multi-task setting differs
\section{RNN/LSTM/Transformer text processing/generation}
Depending on what may be used

\chapter{Tasks}
What has been done when solving these tasks/history/formal definition
\section{Image classification}
Cover some results on similar datasets and their approaches, maybe show that old SIFT/HOG features don't really work vs CNN
\subsection{Transfer learning}
\subsection{ResNet}
\subsection{EfficientNet}
\section{Object detection}
Based on what is going to be detected, maybe text?
\section{Paragraph captioning}
Assuming we are doing this
\section{Multi task learning}
Cover some examples of MTL in Computer Vision

\chapter{Datasets}
Describing our data
\section{Data formats}
Describe what datasets are used for each of the tasks and where they are from etc.

\chapter{Experiments}
Here are our experiments
\section{Training process}
\subsection{Evaluation criterias}
eval
\section{Image classifiers}
Results of image classsifiers on the datasets maybe compare ResNet vs EfficientNet
\subsection{Only transfer learned classifier}
Just a ResNet or something
\subsection{Image classifier with attention}
Add attention to image classifier
\subsection{Classifiers combined to a multi-task model}
How it do
\section{Object detection}
Some stuff for object detection
\section{Multi-task models}
Create multi-task models for all and try to find some pairs/tuples that actually work together properly
\chapter{Result analysis}
Incredible models absolutely.

\chapter{Future work}
How to make it better what could be tried

@@

@misc{knuthwebsite,
    author    = "Donald Knuth",
    title     = "Knuth: Computers and Typesetting",
    url       = "http://www-cs-faculty.stanford.edu/%7Eknuth/abcde.html"
}
1
\end{verbatim}
